---
output: 
    pdf_document:
        fig_caption: yes
        number_sections: true
fontsize: 12pt
geometry: margin=1in
bibliography: References.bib
csl: harvard.csl
header-includes:
- \usepackage{placeins}
- \usepackage{fancyhdr}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
- \usepackage{setspace}\onehalfspacing
---

\pagenumbering{gobble}

```{r child = 'titlepage.Rmd'}
```


\newpage
\pagestyle{fancy}
\fancyhead[LE,RO]{}
\fancyhead[LO,RE]{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

\pagenumbering{roman}

\fancyhead[CO,CE]{Declaration}
\addcontentsline{toc}{section}{Declaration}
\section*{Declaration}

```{r child = 'declaration.Rmd'}
```

```{r include=FALSE}
knitr::opts_chunk$set(fig.path = 'figures/',
                      echo = FALSE, warning = FALSE, message = FALSE)
```


\newpage
\fancyhead[CO,CE]{Abstract}
\addcontentsline{toc}{section}{Abstract}
\section*{Abstract}

```{r child = 'abstract.Rmd'}
```


\newpage
\fancyhead[CO,CE]{Opsomming}
\addcontentsline{toc}{section}{Opsomming}
\section*{Opsomming}
```{r child = 'opsomming.Rmd'}
```


\newpage
\fancyhead[CO,CE]{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}
\section*{Acknowledgements}
```{r child = 'acknowledgements.Rmd'}
```

\newpage
\addcontentsline{toc}{section}{Table of Contents}
\fancyhead[CO,CE]{Table of Contents}
\tableofcontents
\setcounter{tocdepth}{3}

\newpage
\fancyhead[CO,CE]{List of Figures}
\listoffigures
\addcontentsline{toc}{section}{List of Figures}

\newpage
\fancyhead[CO,CE]{List of Tables}
\listoftables
\addcontentsline{toc}{section}{List of Tables}

\newpage
\fancyhead[CO,CE]{Introduction}
\pagenumbering{arabic}

```{r child = 'chapter1.Rmd'}
```


\FloatBarrier
\newpage
\fancyhead[CO,CE]{Art Prices}

```{r child = 'chapter2.Rmd'}
```


\FloatBarrier
\newpage
\fancyhead[CO,CE]{Business Sentiment}

```{r child = 'chapter3.Rmd'}
```


\FloatBarrier
\newpage
\fancyhead[CO,CE]{Historical Commodity Prices}

```{r child = 'chapter4.Rmd'}
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Conclusion}

```{r child = 'chapter5.Rmd'}
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{References}

#References

